\textbf{Selective DNA and Protein Isolation from Marine Macrophyte Surfaces}

### 2020-04-20 submission/manuscript.tex
Added chloroplast plot.

An aliquot of isolated DNA was treated with RNase A (final concentration
200 \si{\ug\per\ml}) for 2 \si{\hour} at 37 \si{\degreeCelsius}. The DNA
concentration was determined using the Quant-iT PicoGreen dsDNA Assay
Kit (Invitrogen, USA) according to the manufacturer's instructions and
diluted to 1 \si{\ng\per\ul}. The V4 region of the 16S rRNA gene was
amplified using a two-step PCR procedure. In the first PCR the 515F
(5'-GTGYCAGCMGCCGCGGTAA-3') and 806R (5'-GGACTACNVGGGTWTCTAAT-3')
primers from the Earth Microbiome Project
(\url{http://press.igsb.anl.gov/earthmicrobiome/protocols-and-standards/16s/})
were used to amplify the target region (Caporaso \emph{et al.}, 2012;
Apprill \emph{et al.}, 2015; Parada \emph{et al.}, 2016). These primers
contained on their 5' end a tagged sequence. Each sample was amplified
in four parallel 25 \si{\ul} reactions of which each contained: 1 × Q5
Reaction Buffer , 0.2 \si{\milli\Molar} of dNTPmix, 0.7 \si{\mg\per\ml}
BSA (Bovine Serum Albumin), 0.2 \si{\micro\Molar} of forward and reverse
primers, 0.5 U of Q5 High-Fidelity DNA Polymerase (New England Biolabs,
USA) and 5 \si{\ng} of DNA template. Cycling conditions were: initial
denaturation at 94 \si{\degreeCelsius} for 3 \si{\minute}, 20 cycles of
denaturation at 94 \si{\degreeCelsius} for 45 \si{\s}, annealing at 50
\si{\degreeCelsius} for 60 \si{\s} and elongation at 72
\si{\degreeCelsius} for 90 \si{\s}, finalized by an elongation step at
72 \si{\degreeCelsius} for 10 \si{\minute}. The four parallel reactions
volumes were pooled and PCR products were purified using the GeneJET PCR
Purification Kit (Thermo Fisher Scientific, USA) according to the
manufacturer's instructions and following the protocol that included
isopropanol addition for better small DNA fragment yield. The column was
eluted in 30 \si{\ul} of deionized water. Purified PCR products were
sent for Illumina MiSeq sequencing (2 × 250 bp) at IMGM Laboratories,
Martinsried, Germany. Before sequencing, at IMGM the second PCR
amplification of the two-step PCR procedure was performed using primers
targeting the tagged region incorporated in the first PCR. In addition,
these primers contained adapter and sample-specific index sequences. The
second PCR was carried out for 8 cycles. Beside samples, a positive and
negative control were sequenced. A negative control was comprised of
four parallel PCR reactions without DNA template, while for a positive
control a mock community composed of evenly mixed DNA material
originating from 20 bacterial strains (ATCC MSA-1002, ATCC, USA) was
used. The sequences obtained in this study have been submitted to the
European Nucleotide Archive (ENA) under accession numbers \textbf{TO BE
ADDED LATER!}.

@@

Obtained sequences were analyzed on the computer cluster Isabella
(University Computing Center, University of Zagreb) using mothur
(version 1.43.0) (Schloss \emph{et al.}, 2009) according to the MiSeq
Standard Operating Procedure (MiSeq SOP;
\url{https://mothur.org/wiki/MiSeq_SOP}) (Kozich \emph{et al.}, 2013)
and recommendations given from the Riffomonas project to enhance data
reproducibility (\url{http://www.riffomonas.org/}). For alignment and
classification of sequences the SILVA SSU Ref NR 99 database (release
138; \url{http://www.arb-silva.de}) was used (Quast \emph{et al.}, 2013;
Yilmaz \emph{et al.}, 2014). Sequences classified as chloroplasts by
mothur were exported, aligned using SILVA incremental aligner (SINA,
version 1.6.0) (Pruesse \emph{et al.}, 2012) against the same SILVA SSU
Ref NR 99 database (release 138) and imported into ARB (version 6.0.6)
(Ludwig \emph{et al.}, 2004) for further phylogenetic analysis using the
same database. Reference sequences close to imported ones were selected
and used to calculate a phylogenetic tree using the Maximum Likelihood
algorithm RAxML (version 7.0.3) with 1000 tree replicates (Stamatakis,
2006). Imported partial chloroplast sequences were added to the tree
using the maximum parsimony criteria and not allowing changes to tree
topology. Pipeline data processing and visualization was done using R
(version 3.6.0) (R Core Team, 2019), package tidyverse (version 1.2.1)
(Wickham \emph{et al.}, 2019) and multiple other packages (Xie, 2014,
2015, 2019a, 2019b; Xie \emph{et al.}, 2018; Zhu, 2019; Allaire \emph{et
al.}, 2019). The detailed analysis procedure including the R Markdown
file for this paper are available as a GitHub repository (\textbf{TO BE
ADDED LATER!}). Based on the ATCC MSA-1002 mock community included in
the analysis a sequencing error rate of 0.009 \si{\percent} was
determined, which is in line with previously reported values for
next-generation sequencing data (Kozich \emph{et al.}, 2013; Schloss
\emph{et al.}, 2016). In addition, the negative control processed
together with the samples yielded only 2 sequences after sequence
quality curation.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Allaire2019}{}%
Allaire, J.J., Xie, Y., McPherson, J., Luraschi, J., Ushey, K., Atkins,
A., et al. (2019) rmarkdown: Dynamic Documents for R.

\leavevmode\hypertarget{ref-Amann1995}{}%
Amann, R.I., Ludwig, W., and Schleifer, K.H. (1995) Phylogenetic
identification and in situ detection of individual microbial cells
without cultivation. \emph{Microbiological reviews} \textbf{59}:
143--169.

\leavevmode\hypertarget{ref-Andersson2010}{}%
Andersson, A.F., Riemann, L., and Bertilsson, S. (2010) Pyrosequencing
reveals contrasting seasonal dynamics of taxa within Baltic Sea
bacterioplankton communities. \emph{The ISME journal} \textbf{4}:
171--181.

\leavevmode\hypertarget{ref-Apprill2015}{}%
Apprill, A., McNally, S., Parsons, R., and Weber, L. (2015) Minor
revision to V4 region SSU rRNA 806R gene primer greatly increases
detection of SAR11 bacterioplankton. \emph{Aquatic Microbial Ecology}
\textbf{75}: 129--137.

\leavevmode\hypertarget{ref-Burke2009}{}%
Burke, C., Kjelleberg, S., and Thomas, T. (2009) Selective extraction of
bacterial DNA from the surfaces of macroalgae. \emph{Applied and
environmental microbiology} \textbf{75}: 252--256.

\leavevmode\hypertarget{ref-Burke2011a}{}%
Burke, C., Steinberg, P., Rusch, D., Kjelleberg, S., and Thomas, T.
(2011) Bacterial community assembly based on functional genes rather
than species. \emph{Proceedings of the National Academy of Sciences of
the United States of America} \textbf{108}: 14288--14293.

\leavevmode\hypertarget{ref-Burke2011b}{}%
Burke, C., Thomas, T., Lewis, M., Steinberg, P., and Kjelleberg, S.
(2011) Composition, uniqueness and variability of the epiphytic
bacterial community of the green alga Ulva australis. \emph{The ISME
journal} \textbf{5}: 590--600.

\leavevmode\hypertarget{ref-Cai2014}{}%
Cai, X., Gao, G., Yang, J., Tang, X., Dai, J., Chen, D., and Song, Y.
(2014) An ultrasonic method for separation of epiphytic microbes from
freshwater submerged macrophytes. \emph{Journal of basic microbiology}
\textbf{54}: 758--761.

\leavevmode\hypertarget{ref-Caporaso2012}{}%
Caporaso, J.G., Lauber, C.L., Walters, W.A., Berg-Lyons, D., Huntley,
J., Fierer, N., et al. (2012) Ultra-high-throughput microbial community
analysis on the Illumina HiSeq and MiSeq platforms. \emph{The ISME
Journal} \textbf{6}: 1621--1624.

\leavevmode\hypertarget{ref-Chourey2010}{}%
Chourey, K., Jansson, J., VerBerkmoes, N., Shah, M., Chavarria, K.L.,
Tom, L.M., et al. (2010) Direct Cellular Lysis/Protein Extraction
Protocol for Soil Metaproteomics. \emph{Journal of Proteome Research}
\textbf{9}: 6615--6622.

\leavevmode\hypertarget{ref-Egan2013}{}%
Egan, S., Harder, T., Burke, C., Steinberg, P., Kjelleberg, S., and
Thomas, T. (2013) The seaweed holobiont: understanding seaweed-bacteria
interactions. \emph{FEMS microbiology reviews} \textbf{37}: 462--476.

\leavevmode\hypertarget{ref-Gilbert2009}{}%
Gilbert, J.A., Field, D., Swift, P., Newbold, L., Oliver, A., Smyth, T.,
et al. (2009) The seasonal structure of microbial communities in the
Western English Channel. \emph{Environmental Microbiology} \textbf{11}:
3132--3139.

@@

\leavevmode\hypertarget{ref-Jiang2015}{}%
Jiang, Y.-F., Ling, J., Dong, J.-D., Chen, B., Zhang, Y.-Y., Zhang,
Y.-Z., and Wang, Y.-S. (2015) Illumina-based analysis the microbial
diversity associated with Thalassia hemprichii in Xincun Bay, South
China Sea. \emph{Ecotoxicology (London, England)} \textbf{24}: 1548--56.

\leavevmode\hypertarget{ref-Kozich2013}{}%
Kozich, J.J., Westcott, S.L., Baxter, N.T., Highlander, S.K., and
Schloss, P.D. (2013) Development of a dual-index sequencing strategy and
curation pipeline for analyzing amplicon sequence data on the MiSeq
Illumina sequencing platform. \emph{Applied and environmental
microbiology} \textbf{79}: 5112--5120.

\leavevmode\hypertarget{ref-Longford2007}{}%
Longford, S., Tujula, N., Crocetti, G., Holmes, A., Holmström, C.,
Kjelleberg, S., et al. (2007) Comparisons of diversity of bacterial
communities associated with three sessile marine eukaryotes.
\emph{Aquatic Microbial Ecology} \textbf{48}: 217--229.

\leavevmode\hypertarget{ref-Ludwig2004}{}%
Ludwig, W., Strunk, O., Westram, R., Richter, L., Meier, H., Yadhukumar,
et al. (2004) ARB: a software environment for sequence data.
\emph{Nucleic Acids Research} \textbf{32}: 1363--1371.

\leavevmode\hypertarget{ref-Massana1997}{}%
Massana, R., Murray, A.E., Preston, C.M., and DeLong, E.F. (1997)
Vertical distribution and phylogenetic characterization of marine
planktonic Archaea in the Santa Barbara Channel. \emph{Applied and
environmental microbiology} \textbf{63}: 50--56.

\leavevmode\hypertarget{ref-Noges2010}{}%
Nõges, T., Luup, H., and Feldmann, T. (2010) Primary production of
aquatic macrophytes and their epiphytes in two shallow lakes (Peipsi and
Võrtsjärv) in Estonia. \emph{Aquatic Ecology} \textbf{44}: 83--92.

\leavevmode\hypertarget{ref-Parada2016}{}%
Parada, A.E., Needham, D.M., and Fuhrman, J.A. (2016) Every base
matters: assessing small subunit rRNA primers for marine microbiomes
with mock communities, time series and global field samples.
\emph{Environmental Microbiology} \textbf{18}: 1403--1414.

\leavevmode\hypertarget{ref-Pruesse2012}{}%
Pruesse, E., Peplies, J., and Glöckner, F.O. (2012) SINA: accurate
high-throughput multiple sequence alignment of ribosomal RNA genes.
\emph{Bioinformatics (Oxford, England)} \textbf{28}: 1823--1829.

\leavevmode\hypertarget{ref-Quast2013}{}%
Quast, C., Pruesse, E., Yilmaz, P., Gerken, J., Schweer, T., Yarza, P.,
et al. (2013) The SILVA ribosomal RNA gene database project: improved
data processing and web-based tools. \emph{Nucleic acids research}
\textbf{41}: D590--6.

\leavevmode\hypertarget{ref-RCoreTeam2019}{}%
R Core Team (2019) R: A Language and Environment for Statistical
Computing, Vienna, Austria: R Foundation for Statistical Computing.

\leavevmode\hypertarget{ref-Richter-Heitmann2016}{}%
Richter-Heitmann, T., Eickhorst, T., Knauth, S., Friedrich, M.W., and
Schmidt, H. (2016) Evaluation of Strategies to Separate Root-Associated
Microbial Communities: A Crucial Choice in Rhizobiome Research.
\emph{Frontiers in Microbiology} \textbf{7}: 773.

\leavevmode\hypertarget{ref-Schloss2016}{}%
Schloss, P.D., Girard, R.A., Martin, T., Edwards, J., and Thrash, J.C.
(2016) Status of the Archaeal and Bacterial Census: an Update.
\emph{mBio} \textbf{7}: e00201--16.

\leavevmode\hypertarget{ref-Schloss2009}{}%
Schloss, P.D., Westcott, S.L., Ryabin, T., Hall, J.R., Hartmann, M.,
Hollister, E.B., et al. (2009) Introducing mothur: open-source,
platform-independent, community-supported software for describing and
comparing microbial communities. \emph{Applied and environmental
microbiology} \textbf{75}: 7537--7541.

\leavevmode\hypertarget{ref-Stamatakis2006}{}%
Stamatakis, A. (2006) RAxML-VI-HPC: maximum likelihood-based
phylogenetic analyses with thousands of taxa and mixed models.
\emph{Bioinformatics} \textbf{22}: 2688--2690.

\leavevmode\hypertarget{ref-Staufenberger2008}{}%
Staufenberger, T., Thiel, V., Wiese, J., and Imhoff, J.F. (2008)
Phylogenetic analysis of bacteria associated with Laminaria saccharina.
\emph{FEMS Microbiology Ecology} \textbf{64}: 65--77.

\leavevmode\hypertarget{ref-Su2012}{}%
Su, C., Lei, L., Duan, Y., Zhang, K.-Q., and Yang, J. (2012)
Culture-independent methods for studying environmental microorganisms:
methods, application, and perspective. \emph{Applied microbiology and
biotechnology} \textbf{93}: 993--1003.

\leavevmode\hypertarget{ref-Uku2007}{}%
Uku, J., Björk, M., Bergman, B., and Díez, B. (2007) Characterization
and comparison of prokaryotic epiphytes associated with three East
African seagrasses. \emph{Journal of Phycology} \textbf{43}: 768--779.

\leavevmode\hypertarget{ref-Weidner1996}{}%
Weidner, S., Arnold, W., and Puhler, A. (1996) Diversity of uncultured
microorganisms associated with the seagrass Halophila stipulacea
estimated by restriction fragment length polymorphism analysis of
PCR-amplified 16S rRNA genes. \emph{Applied and environmental
microbiology} \textbf{62}: 766--771.

\leavevmode\hypertarget{ref-Wickham2019}{}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.D., François,
R., et al. (2019) Welcome to the tidyverse. \emph{Journal of Open Source
Software} \textbf{4}: 1686.

\leavevmode\hypertarget{ref-Wisniewski2009}{}%
Wiśniewski, J.R., Zougman, A., Nagaraj, N., and Mann, M. (2009)
Universal sample preparation method for proteome analysis. \emph{Nature
Methods} \textbf{6}: 359--362.

\leavevmode\hypertarget{ref-Xie2015}{}%
Xie, Y. (2015) Dynamic Documents with \{R\} and knitr, 2nd ed. Boca
Raton, Florida: Chapman; Hall/CRC.

\leavevmode\hypertarget{ref-Xie2014}{}%
Xie, Y. (2014) knitr: A Comprehensive Tool for Reproducible Research in
\{R\}. In \emph{Implementing reproducible computational research}.
Stodden, V., Leisch, F., and Peng, R.D. (eds). Chapman; Hall/CRC.

\leavevmode\hypertarget{ref-Xie2019a}{}%
Xie, Y. (2019a) knitr: A General-Purpose Package for Dynamic Report
Generation in R.

\leavevmode\hypertarget{ref-Xie2019}{}%
Xie, Y. (2019b) tinytex: Helper Functions to Install and Maintain 'TeX
Live', and Compile 'LaTeX' Documents.

\leavevmode\hypertarget{ref-Xie2018}{}%
Xie, Y., Allaire, J.J., and Grolemund, G. (2018) R Markdown: The
Definitive Guide, Boca Raton, Florida: Chapman; Hall/CRC.

\leavevmode\hypertarget{ref-Yilmaz2014}{}%
Yilmaz, P., Parfrey, L.W., Yarza, P., Gerken, J., Pruesse, E., Quast,
C., et al. (2014) The SILVA and "All-species Living Tree Project (LTP)"
taxonomic frameworks. \emph{Nucleic acids research} \textbf{42}:
D643--8.

\leavevmode\hypertarget{ref-Zhu2019}{}%
Zhu, H. (2019) kableExtra: Construct Complex Table with 'kable' and Pipe
Syntax.

@@

@@

>>>>

An aliquot of isolated DNA was treated with RNase A (final concentration
200 \si{\ug\per\ml}) for 2 \si{\hour} at 37 \si{\degreeCelsius}. The DNA
concentration was determined using the Quant-iT PicoGreen dsDNA Assay
Kit (Invitrogen, USA) according to the manufacturer's instructions and
diluted to 1 \si{\ng\per\ul}. The V4 region of the 16S rRNA gene was
amplified using a two-step PCR procedure. In the first PCR the 515F
(5'-GTGYCAGCMGCCGCGGTAA-3') and 806R (5'-GGACTACNVGGGTWTCTAAT-3')
primers from the Earth Microbiome Project
(\url{http://press.igsb.anl.gov/earthmicrobiome/protocols-and-standards/16s/})
were used to amplify the target region (Caporaso \emph{et al.}, 2012;
Apprill \emph{et al.}, 2015; Parada \emph{et al.}, 2016). These primers
contained on their 5' end a tagged sequence. Each sample was amplified
in four parallel 25 \si{\ul} reactions of which each contained: 1 × Q5
Reaction Buffer , 0.2 \si{\milli\Molar} of dNTPmix, 0.7 \si{\mg\per\ml}
BSA (Bovine Serum Albumin), 0.2 \si{\micro\Molar} of forward and reverse
primers, 0.5 U of Q5 High-Fidelity DNA Polymerase (New England Biolabs,
USA) and 5 \si{\ng} of DNA template. Cycling conditions were: initial
denaturation at 94 \si{\degreeCelsius} for 3 \si{\minute}, 20 cycles of
denaturation at 94 \si{\degreeCelsius} for 45 \si{\s}, annealing at 50
\si{\degreeCelsius} for 60 \si{\s} and elongation at 72
\si{\degreeCelsius} for 90 \si{\s}, finalized by an elongation step at
72 \si{\degreeCelsius} for 10 \si{\minute}. The four parallel reactions
volumes were pooled and PCR products were purified using the GeneJET PCR
Purification Kit (Thermo Fisher Scientific, USA) according to the
manufacturer's instructions and following the protocol that included
isopropanol addition for better small DNA fragment yield. The column was
eluted in 30 \si{\ul} of deionized water. Purified PCR products were
sent for Illumina MiSeq sequencing (2 × 250 bp) at IMGM Laboratories,
Martinsried, Germany. Before sequencing, at IMGM the second PCR
amplification of the two-step PCR procedure was performed using primers
targeting the tagged region incorporated in the first PCR. In addition,
these primers contained adapter and sample-specific index sequences. The
second PCR was carried out for 8 cycles. Beside samples, a positive and
negative control were sequenced. A negative control was comprised of
four parallel PCR reactions without DNA template, while for a positive
control a mock community composed of evenly mixed DNA material
originating from 20 bacterial strains (ATCC MSA-1002, ATCC, USA) was
used. Sequences obtained in this study have been deposited in the
European Nucleotide Archive (ENA) at EMBL-EBI under accession numbers
SAMEA6786270, SAMEA6648792 -- SAMEA6648794, SAMEA6648809 --
SAMEA6648811.

@@

Obtained sequences were analyzed on the computer cluster Isabella
(University Computing Center, University of Zagreb) using mothur
(version 1.43.0) (Schloss \emph{et al.}, 2009) according to the MiSeq
Standard Operating Procedure (MiSeq SOP;
\url{https://mothur.org/wiki/MiSeq_SOP}) (Kozich \emph{et al.}, 2013)
and recommendations given from the Riffomonas project to enhance data
reproducibility (\url{http://www.riffomonas.org/}). For alignment and
classification of sequences the SILVA SSU Ref NR 99 database (release
138; \url{http://www.arb-silva.de}) was used (Quast \emph{et al.}, 2013;
Yilmaz \emph{et al.}, 2014). Sequences classified as chloroplasts by
SILVA were exported and reclassifed using mothur and the RDP (Ribosomal
Database Project; \url{http://rdp.cme.msu.edu/}) training set (version
16) reference files adapted for mothur (Cole \emph{et al.}, 2014). In
comparison to SILVA, RDP allows a more detailed classification of
chloroplast sequences. Pipeline data processing and visualization was
done using R (version 3.6.0) (R Core Team, 2019), package tidyverse
(version 1.3.0) (Wickham \emph{et al.}, 2019) and multiple other
packages (Xie, 2014, 2015, 2019b, 2019a, 2020; Neuwirth, 2014; Xie
\emph{et al.}, 2018; Allaire \emph{et al.}, 2019; Zhu, 2019). The
detailed analysis procedure including the R Markdown file for this paper
are available as a GitHub repository
(\url{https://github.com/mkorlevic/Korlevic_SelectiveRemoval_EnvironMicrobiol_2020}).
Based on the ATCC MSA-1002 mock community included in the analysis a
sequencing error rate of 0.009 \si{\percent} was determined, which is in
line with previously reported values for next-generation sequencing data
(Kozich \emph{et al.}, 2013; Schloss \emph{et al.}, 2016). In addition,
the negative control processed together with the samples yielded only 2
sequences after sequence quality curation.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Allaire2019}{}%
Allaire, J.J., Xie, Y., McPherson, J., Luraschi, J., Ushey, K., Atkins,
A., et al. (2019) Rmarkdown: Dynamic documents for R.

\leavevmode\hypertarget{ref-Amann1995}{}%
Amann, R.I., Ludwig, W., and Schleifer, K.H. (1995) Phylogenetic
identification and \emph{in situ} detection of individual microbial
cells without cultivation. \emph{Microbiol Rev} \textbf{59}: 143--169.

\leavevmode\hypertarget{ref-Andersson2010}{}%
Andersson, A.F., Riemann, L., and Bertilsson, S. (2010) Pyrosequencing
reveals contrasting seasonal dynamics of taxa within Baltic Sea
bacterioplankton communities. \emph{ISME J} \textbf{4}: 171--181.

\leavevmode\hypertarget{ref-Apprill2015}{}%
Apprill, A., McNally, S., Parsons, R., and Weber, L. (2015) Minor
revision to V4 region SSU rRNA 806R gene primer greatly increases
detection of SAR11 bacterioplankton. \emph{Aquat Microb Ecol}
\textbf{75}: 129--137.

\leavevmode\hypertarget{ref-Burke2009}{}%
Burke, C., Kjelleberg, S., and Thomas, T. (2009) Selective extraction of
bacterial DNA from the surfaces of macroalgae. \emph{Appl Environ
Microbiol} \textbf{75}: 252--256.

\leavevmode\hypertarget{ref-Burke2011}{}%
Burke, C., Steinberg, P., Rusch, D., Kjelleberg, S., and Thomas, T.
(2011) Bacterial community assembly based on functional genes rather
than species. \emph{Proc Natl Acad Sci U S A} \textbf{108}:
14288--14293.

\leavevmode\hypertarget{ref-Burke2011a}{}%
Burke, C., Thomas, T., Lewis, M., Steinberg, P., and Kjelleberg, S.
(2011) Composition, uniqueness and variability of the epiphytic
bacterial community of the green alga \emph{Ulva australis}. \emph{ISME
J} \textbf{5}: 590--600.

\leavevmode\hypertarget{ref-Cai2014}{}%
Cai, X., Gao, G., Yang, J., Tang, X., Dai, J., Chen, D., and Song, Y.
(2014) An ultrasonic method for separation of epiphytic microbes from
freshwater submerged macrophytes. \emph{J Basic Microbiol} \textbf{54}:
758--761.

\leavevmode\hypertarget{ref-Caporaso2012}{}%
Caporaso, J.G., Lauber, C.L., Walters, W.A., Berg-Lyons, D., Huntley,
J., Fierer, N., et al. (2012) Ultra-high-throughput microbial community
analysis on the Illumina HiSeq and MiSeq platforms. \emph{ISME J}
\textbf{6}: 1621--1624.

\leavevmode\hypertarget{ref-Chourey2010}{}%
Chourey, K., Jansson, J., VerBerkmoes, N., Shah, M., Chavarria, K.L.,
Tom, L.M., et al. (2010) Direct cellular lysis/protein extraction
protocol for soil metaproteomics. \emph{J Proteome Res} \textbf{9}:
6615--6622.

\leavevmode\hypertarget{ref-Cole2014}{}%
Cole, J.R., Wang, Q., Fish, J.A., Chai, B., McGarrell, D.M., Sun, Y., et
al. (2014) Ribosomal Database Project: Data and tools for high
throughput rRNA analysis. \emph{Nucleic Acids Res} \textbf{42}:
D633--D642.

\leavevmode\hypertarget{ref-Egan2013}{}%
Egan, S., Harder, T., Burke, C., Steinberg, P., Kjelleberg, S., and
Thomas, T. (2013) The seaweed holobiont: Understanding seaweed-bacteria
interactions. \emph{FEMS Microbiol Rev} \textbf{37}: 462--476.

\leavevmode\hypertarget{ref-Gilbert2009}{}%
Gilbert, J.A., Field, D., Swift, P., Newbold, L., Oliver, A., Smyth, T.,
et al. (2009) The seasonal structure of microbial communities in the
Western English Channel. \emph{Environ Microbiol} \textbf{11}:
3132--3139.

@@

\leavevmode\hypertarget{ref-Jiang2015}{}%
Jiang, Y.-F., Ling, J., Dong, J.-D., Chen, B., Zhang, Y.-Y., Zhang,
Y.-Z., and Wang, Y.-S. (2015) Illumina-based analysis the microbial
diversity associated with \emph{Thalassia hemprichii} in Xincun Bay,
South China Sea. \emph{Ecotoxicology} \textbf{24}: 1548--56.

\leavevmode\hypertarget{ref-Kozich2013}{}%
Kozich, J.J., Westcott, S.L., Baxter, N.T., Highlander, S.K., and
Schloss, P.D. (2013) Development of a dual-index sequencing strategy and
curation pipeline for analyzing amplicon sequence data on the MiSeq
Illumina sequencing platform. \emph{Appl Environ Microbiol} \textbf{79}:
5112--5120.

\leavevmode\hypertarget{ref-Longford2007}{}%
Longford, S., Tujula, N., Crocetti, G., Holmes, A., Holmström, C.,
Kjelleberg, S., et al. (2007) Comparisons of diversity of bacterial
communities associated with three sessile marine eukaryotes. \emph{Aquat
Microb Ecol} \textbf{48}: 217--229.

\leavevmode\hypertarget{ref-Massana1997}{}%
Massana, R., Murray, A.E., Preston, C.M., and DeLong, E.F. (1997)
Vertical distribution and phylogenetic characterization of marine
planktonic \emph{Archaea} in the Santa Barbara Channel. \emph{Appl
Environ Microbiol} \textbf{63}: 50--56.

\leavevmode\hypertarget{ref-Neuwirth2014}{}%
Neuwirth, E. (2014) RColorBrewer: ColorBrewer palettes.

\leavevmode\hypertarget{ref-Noges2010}{}%
Nõges, T., Luup, H., and Feldmann, T. (2010) Primary production of
aquatic macrophytes and their epiphytes in two shallow lakes (Peipsi and
Võrtsjärv) in Estonia. \emph{Aquat Ecol} \textbf{44}: 83--92.

\leavevmode\hypertarget{ref-Parada2016}{}%
Parada, A.E., Needham, D.M., and Fuhrman, J.A. (2016) Every base
matters: Assessing small subunit rRNA primers for marine microbiomes
with mock communities, time series and global field samples.
\emph{Environ Microbiol} \textbf{18}: 1403--1414.

\leavevmode\hypertarget{ref-Quast2013}{}%
Quast, C., Pruesse, E., Yilmaz, P., Gerken, J., Schweer, T., Yarza, P.,
et al. (2013) The SILVA ribosomal RNA gene database project: Improved
data processing and web-based tools. \emph{Nucleic Acids Res}
\textbf{41}: D590--D596.

\leavevmode\hypertarget{ref-RCoreTeam2019}{}%
R Core Team (2019) A language and environment for statistical computing,
Vienna, Austria: R Foundation for Statistical Computing.

\leavevmode\hypertarget{ref-Richter-Heitmann2016}{}%
Richter-Heitmann, T., Eickhorst, T., Knauth, S., Friedrich, M.W., and
Schmidt, H. (2016) Evaluation of strategies to separate root-associated
microbial communities: A crucial choice in rhizobiome research.
\emph{Front Microbiol} \textbf{7}: 773.

\leavevmode\hypertarget{ref-Schloss2016}{}%
Schloss, P.D., Jenior, M.L., Koumpouras, C.C., Westcott, S.L., and
Highlander, S.K. (2016) Sequencing 16S rRNA gene fragments using the
PacBio SMRT DNA sequencing system. \emph{PeerJ} \textbf{4}: e1869.

\leavevmode\hypertarget{ref-Schloss2009}{}%
Schloss, P.D., Westcott, S.L., Ryabin, T., Hall, J.R., Hartmann, M.,
Hollister, E.B., et al. (2009) Introducing mothur: Open-source,
platform-independent, community-supported software for describing and
comparing microbial communities. \emph{Appl Environ Microbiol}
\textbf{75}: 7537--7541.

\leavevmode\hypertarget{ref-Staufenberger2008}{}%
Staufenberger, T., Thiel, V., Wiese, J., and Imhoff, J.F. (2008)
Phylogenetic analysis of bacteria associated with \emph{Laminaria
saccharina}. \emph{FEMS Microbiol Ecol} \textbf{64}: 65--77.

\leavevmode\hypertarget{ref-Su2012}{}%
Su, C., Lei, L., Duan, Y., Zhang, K.-Q., and Yang, J. (2012)
Culture-independent methods for studying environmental microorganisms:
Methods, application, and perspective. \emph{Appl Microbiol Biotechnol}
\textbf{93}: 993--1003.

\leavevmode\hypertarget{ref-Uku2007}{}%
Uku, J., Björk, M., Bergman, B., and Díez, B. (2007) Characterization
and comparison of prokaryotic epiphytes associated with three East
African seagrasses. \emph{J Phycol} \textbf{43}: 768--779.

\leavevmode\hypertarget{ref-Weidner1996}{}%
Weidner, S., Arnold, W., and Puhler, A. (1996) Diversity of uncultured
microorganisms associated with the seagrass \emph{Halophila stipulacea}
estimated by restriction fragment length polymorphism analysis of
PCR-amplified 16S rRNA genes. \emph{Appl Environ Microbiol} \textbf{62}:
766--771.

\leavevmode\hypertarget{ref-Wickham2019}{}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.D., François,
R., et al. (2019) Welcome to the tidyverse. \emph{J Open Source Softw}
\textbf{4}: 1686.

\leavevmode\hypertarget{ref-Wisniewski2009}{}%
Wiśniewski, J.R., Zougman, A., Nagaraj, N., and Mann, M. (2009)
Universal sample preparation method for proteome analysis. \emph{Nat
Methods} \textbf{6}: 359--362.

\leavevmode\hypertarget{ref-Xie2015}{}%
Xie, Y. (2015) Dynamic Documents with R and knitr, 2nd ed. Boca Raton,
Florida: Chapman and Hall/CRC.

\leavevmode\hypertarget{ref-Xie2014}{}%
Xie, Y. (2014) Knitr: A comprehensive tool for reproducible research in
R. In \emph{Implementing Reproducible Computational Research}. Stodden,
V., Leisch, F., and Peng, R.D. (eds). New York: Chapman and Hall/CRC,
pp. 3--32.

\leavevmode\hypertarget{ref-Xie2019}{}%
Xie, Y. (2019a) Knitr: A general-purpose package for dynamic report
generation in R.

\leavevmode\hypertarget{ref-Xie2019a}{}%
Xie, Y. (2019b) TinyTeX: A lightweight, cross-platform, and
easy-to-maintain LaTeX distribution based on TeX Live. \emph{TUGboat}
\textbf{40}: 30--32.

\leavevmode\hypertarget{ref-Xie2020}{}%
Xie, Y. (2020) TinyTex: Helper functions to install and maintain 'TeX
Live', and compile 'LaTeX' documents.

\leavevmode\hypertarget{ref-Xie2018}{}%
Xie, Y., Allaire, J.J., and Grolemund, G. (2018) R Markdown: The
Definitive Guide, 1st ed. Boca Raton, Florida: Chapman and Hall/CRC.

\leavevmode\hypertarget{ref-Yilmaz2014}{}%
Yilmaz, P., Parfrey, L.W., Yarza, P., Gerken, J., Pruesse, E., Quast,
C., et al. (2014) The SILVA and "All-Species Living Tree Project (LTP)"
taxonomic frameworks. \emph{Nucleic Acids Res} \textbf{42}: D643--D648.

\leavevmode\hypertarget{ref-Zhu2019}{}%
Zhu, H. (2019) KableExtra: Construct complex table with 'kable' and pipe
syntax.

@@

\textbf{\autoref{chloroplast}.} \nameref{chloroplast}

@@

{\centering \includegraphics[width=1\linewidth]{../results/figures/chloroplast}

\caption{Taxonomic classification and relative contribution of chloroplast sequences from surfaces of two marine macrophytes (\textit{C. nodosa} and \textit{C. cylindracea}) sampled in the Bay of Saline and the Bay of Funtana (Mixed and Monospecific Settlements) and in two contrasting seasons (4 December 2017 and 19 June 2018).\label{chloroplast}}\label{fig:unnamed-chunk-5}
\end{figure}
